Predicting Levels of Sales for Newly Published Books \\ using Cost-Sensitive Ensemble Methods

### 2016-12-02 paper.tex
Added Boosting subsection

\item \textbf{Boosting}
\item \textbf{Random Forest}
This method is based on the construction of a set of decision trees using a stochastic process over the basis of C4.5 algorithm. It was proposed by Breiman in \cite{Breiman2001} and aims to create independent and uncorrelated trees based on different and random input vectors, following the same distribution. 
The result is the average of the generated trees during the process.
\end{itemize}

>>>>

\item \textbf{Boosting} 
Boosting is an ensemble classification algorithm which was first proposed by \citet{schapire1990strength} in \citet{schapire1990strength}. Boosting is based on the idea that a set of weak classifiers can create a stronger one. In this work we adopt a powerful a variation of boosting called Adaptive Boosting or "Adaboost" for short \cite{FS1997}. Adaboost operates on a training dataset ${(x_{1},y_{1}),...,(x_{m},y_{m})}$ where each $x_{i}$ is a set of inputs belongs to some domain $X$ and each $y_{i}$ belongs to some label $Y$ assuming $Y$ is a binary class set $\{+1,-1\}$.

During the learning process, Adaboost modifies the dataset by weighting its samples. These weights are updated every time a new classifier is trained to increase the focus on the difficult data instances. Consequently, the final generated classifier is a weighted combination of all trained base classifiers. According to many previous works, Adaboost is resistant to overfitting and it can outperform many other state-of-the-art classification techniques.

\item \textbf{Random Forest}
This method is based on the construction of a set of decision trees using a stochastic process over the basis of C4.5 algorithm. It was proposed by Breiman in \cite{Breiman2001} and aims to create independent and uncorrelated trees based on different and random input vectors, following the same distribution. 
The result is the average of the generated trees during the process.
\end{itemize}
